---
title: "DATA 605 Final"
author: "Michael D'Acampora"
date: "May 18, 2018"
output: html_document
---

```{r}
library(dplyr)
house_data <- read.csv('https://raw.githubusercontent.com/mjdacs/data605/master/train.csv', header = TRUE)
head(house_data)
```


Pick one of the quantitative variables from the training set, and define that variable x. Make sure this variable is skewed to the right!

```{r}
hist(house_data$BsmtUnfSF)
```

We see that `GrLivArea` --ground living area (sft)-- has a right skew. Additionally, `SalesPrice` is our chosen dependent variable. 
```{r}

X <- house_data$BsmtUnfSF

Y <- house_data$SalePrice


#house_data <- house_data %>% 
#  rename(X = SalePrice,
#         Y = LotArea) 

#head(house_data)
```

Probability. Calculate as a minimum the belwo probabilities a through c. Assume the small letter 'x' is estimated ast he 1st quartile of the X variable, and the small letter 'y' is the 1st quartile of the Y variable. Interpret the meaning of all probabilities. In addition, make a table of counts as shown below.

We run a summary of `BsmtUnfSF` to confirm the right skew.
```{r}
summary(X)
```

Since the Mean > Median, it confirms the right skew.

We also run a summary of the dependent variable `SalesPrice`, or Y

```{r}
summary(Y)
```
  
  a. $P(X>x~~ | ~~Y>y)$
  
We are asking what is the probability that X variable is greater than its first quartile given that Y is larger than the its second quartile. 
```{r}

#  quartiles for BsmtUnfSF
q1_x <- summary(X)[2]
q2_x <- summary(X)[3]
q3_x <- summary(X)[5]

# quartiles for SalesPrice
q1_x <- summary(Y)[2]
q2_x <- summary(Y)[3]
q3_x <- summary(Y)[5]

```
 
  b. $P(X>x, Y>y)$
  
  c. $P(X<x~~ | ~~Y>y)$