---
title: "Assigment 15"
author: "Michael D'Acampora"
date: "May 13, 2018"
output: html_document
---

**1. Find the equation of the regression line for the given points.  Round any final values to the nearest hundredth, if necessary.**

$$( 5.6, 8.8 ), ( 6.3, 12.4 ), ( 7, 14.8 ), ( 7.7, 18.2 ), ( 8.4, 20.8 )$$
```{r}
x <- c(5.6, 6.3, 7, 7.7, 8.4)
y <- c(8.8, 12.4, 14.8, 18.2, 20.8)

mod <- lm(y ~ x)
mod
```

The equation of the linear regression line is $y = -14.8 + 4.26x$


**2. Find all local maxima, local minima, and saddle points for the function given below. Write your answer(s) in the form (x,y,z). Separate multiple points with a comma.**
$$f(x,y)=24x-6xy^2-8y^3$$

We will take the partial derivative with respect to x and solve for y:

$$\frac{\delta}{\delta x}=24-6y^2=0$$

$$y^2=4; ~~~y=2, y=-2$$

Now we take solutions for y and solve for the partial derivative with respect to x 
$$\frac{\delta}{\delta y}=-12xy-24y^2=xy+2y^2=0$$

Plugging in y=2
$$x(2)+2(2)^2=0$$
$$x=-4$$

Plugging in y=-2
$$x(-2)+2(-2)^2=0$$
$$x=4$$

Critical points are (-4,2) and (4,2)

We need to take the second derivative to find whether the points are minima, maxima, or saddle points.

$$\frac{\delta^2}{\delta x^2}=0$$


$$\frac{\delta^2}{\delta y^2}=-12x-48y^2$$

finding $f_{xy}$:
$$f_{xy}=-12y$$

http://bonlacfoods.com/pdf/018077980.pdf

Classifying stationary points

 if $f_{xx}f_{yy}-f^2_{xy} < 0$ at (a,b), then (a,b) is a saddle point

 if $f_{xx}f_{yy}-f^2_{xy} > 0$ at (a,b), then (a,b) is a maximum or minimum and is distinguished as follows:

  if $f_{xx} < 0$ and $f_{yy} < 0$ at (a,b) then (a,b) is a maximum point

  if $f_{xx} > 0$ and $f_{yy} > 0$ at (a,b) then (a,b) is a minimum point
  

$$D=0*(-12x-48y^2)-(-12y)^2=12y^2$$

At $(4, -2)$:
$D = 12(2)^2>0$ which is a max or min, and $-12(4)-48(-2)^2=-240$ which tells us it is a maxima.

At $(-4,2)$
$D = 12(-2)^2>0$ which is a max or min, and $-12(-4)-48(2)^2=-144$ which tells us it is also a maxima.

**3. A grocery store sells two brands of a product, the "house" brand and a "name" brand.  The manager estimates that if she sells the "house" brand for x dollars and the "name" brand for y dollars, she will be able to sell $81-21x+17y$ of the "house" brand and $40 + 11x - 23y$ units of the "name" brand.**

**Step 1.**
 Find the revenue function $R(x,y)$
 
 $R(x,y) = x(81-21x+17y) + y(40+11x-23y) = 81x - 21X^2 +17xy +40y+11xy - 23y^2$
 
 $$R(x,y) = 81x - 21x^2 + 28xy +40y -23y^2$$


**Step 2.**
What is the revenue if she sells the "house" brand for $2.30 and the "name" brand for \$4.10?
 
```{r}
rev <- function(x,y){
  return(81*x - 21*x^2 + 28*x*y + 40*y - 23*y^2)
}

rev(2.30, 4.10)
```
 

**4. A company has a plant in Los Angeles and a plant in Denver. The firm is committed to produce a total of 96 units of a product each week. The total weekly cost is given by $C(x,y)=\frac{1}{6}x^2+\frac{1}{6}y^2+7x+25y+700$, where x is the number of units produced in Los Angeles and y is the number of units produced in Denver. How many units should be produced in each plant to minimize the total weekly cost?**

To start,

$x+y=96$

$y=96-x$

Plugging in y into C(x,y):

$$C(x,y) = \frac{1}{6} x^2 + \frac{1}{6} (96 - x)^2 + 7x + 25(96-x) + 700$$

$$= \frac{1}{6} x^2 + \frac{9216 -192x + x^2}{6} + 7x + 2400 - 25x + 700$$

$$ = \frac{1}{6} x^2 + 1536 - 32x + \frac{x^2}{6} + 7x + 2400 - 25x + 700$$

$$= \frac{1}{6} x^2 + 1536 - 32x + \frac{x^2}{6} + 7x + 2400 - 25x + 700$$

$$C(x) = \frac{1}{3} x^2 - 50x + 4636$$

Take the derivative to obtain the critcal points,

$$C'(x)=\frac{2}{3}x-50=0$$

$$x=75$$

Now we can plug x into our simple equation and solve for y,

$$x+y=96$$
$$y=96-75=21$$

75 units should be produced in LA, and 21 in Denver.

