---
title: "DATA 605 Assignment 1"
author: "Michael D'Acampora"
date: "February 3, 2018"
output: html_document
---


* Problem Set 1

1. Calculate the dot product u.v where u = [0.5; 0.5] and v = [3; −4]

```{r}
u = c(0.5, 0.5)
v = c(3, -4)
paste("The dot product of u and v is:", u %*% v)
```

2. What are the lengths of u and v? Please note that the mathematical notion of the length of a vector is not the same as a computer science definition.

```{r}
# the formula for the length of a vector is the Pythagorean formula

lenU <-  sqrt(sum(u^2))
lenV <-  sqrt(sum(v^2))
paste("The lengths of u and v are", lenU, "and", lenV, ", respectively")
```

3. What is the linear combination: 3u − 2v?

```{r}
linCombo<- 3 * u - 2 * v
paste(c("The linear combination of 3u - 2v is", linCombo), collapse = " ")

```

4. What is the angle between u and v?

```{r}
theta <- acos(sum(u*v) / (sqrt(sum(u * u)) * sqrt(sum(v * v))))
theta * 180 / pi
```

* Problem Set 2

Set up a system of equations with 3 variables and 3 constraints and solve for x. Please write a function in R that will take two variables (matrix A & constraint vector b) and solve using elimination. Your function should produce the right answer for the system of equations for any 3-variable, 3-equation system. You don’t have to worry about degenerate cases and can safely assume that the function will only be tested with a system of equations that has a solution. Please note that you do have to worry about zero pivots, though. Please note that you should not use the built-in function solve to solve this system or use matrix inverses. The approach that you should employ is to construct an Upper Triangular Matrix and then back-substitute to get the solution. Alternatively, you can augment the matrix A with vector b and jointly apply the Gauss Jordan elimination procedure.

```{r}

# matrix = A
matrix<- matrix(c(1,1,3,2,-1,5,-1,-2,4), 
                      nrow=3,              
                      ncol=3,              
                      byrow = TRUE)        
   
# vector = b
vector <- matrix(c(1,2,6), 
                      nrow=3,              
                      ncol=1,              
                      byrow = TRUE)  
                             
# the function is for a 3x3 matrix
upper.tri.mat <- function(A,b){
  
  # create the augmented matrix by combining matrix A and vector b
  aug.mat <- cbind(A,b)
  
  # start with pivot at value of (1,1)
  pivot1 <- aug.mat[1,1]
  
  # to zero out (2,1), we need to create a multiple by dividing by (1,1) and subtract row 2 from (row 1 * the multiple)
  multiple <- aug.mat[2,1] / pivot1
  aug.mat[2, ] <- aug.mat[2,] - aug.mat[1,] * multiple

  # we do the same thing for row 3, divide by (1,1) and subtract row 3 from (row 1 * the multiple)
  multiple <- aug.mat[3,1] / pivot1
  aug.mat[3, ] <- aug.mat[3, ] - aug.mat[1, ] * multiple
  
  # since we are operating with rows 2 and 3, we need to create a new pivot point with which to create a multiple
  # since 2,1 has been zeroed out we will select 2,2 to work with
  pivot2 <- aug.mat[2,2]
  multiple <- aug.mat[3,2] / pivot2
  aug.mat[3, ] <- aug.mat[3, ] - aug.mat[2, ] * multiple
  
  # now we can solve for x1, x2, and x3
  x3 <- aug.mat[3,4] / aug.mat[3,3]
  x2 <- (aug.mat[2,4] - aug.mat[2,3] * x3) / aug.mat[2,2]
  x1 <- (aug.mat[1,4] - aug.mat[1,3] * x3 - aug.mat[1,2] * x2) / aug.mat[1,1]
  
  solution <- c(x1,x2,x3)
  solution
}


```

Please test it with the system below and it should produce a solution x = [-1.55, -0.32, 0.5]
```{r}
round(upper.tri.mat(matrix, vector),2)
```


























