---
title: "Assignments Week 2"
author: "Michael D'Acampora"
date: "February 11, 2018"
output: html_document
---

#Problem Set 1
#### (1) Show that $A^TA \ne AA^T$ in general.

```{r}
X <-matrix(c(1,1,3,4,1,1,3,2,5),nrow=3)
X
t(X)
X %*% t(X)
t(X) %*% X
```



$$If A = \left[ \begin{array}{ccc} 1 & 4 & 3 \\ 1 & 1 & 2\\3 & 1 & 5\end{array}\right], then~ A^T = \left[ \begin{array}{ccc} 1 & 1 & 3 \\ 4 & 1 & 1\\3 & 2 & 5\end{array}\right]$$

$$AA^T = \left[ \begin{array}{ccc} 1 & 4 & 3 \\ 1 & 1 & 2\\3 & 1 & 5\end{array}\right] \left[ \begin{array}{ccc} 1 & 1 & 3 \\ 4 & 1 & 1\\3 & 2 & 5\end{array}\right] = \left[ \begin{array}{ccc} 26 & 11 & 22 \\ 11 & 6 & 14 \\ 22 & 14 & 35 \end{array}\right]$$
$$A^TA = \left[ \begin{array}{ccc} 1& 1 & 3 \\ 4 & 1 & 1\\3 & 2 & 5\end{array}\right] \left[ \begin{array}{ccc} 1 & 4 & 3 \\ 1 & 1 & 2\\3 & 1 & 5\end{array}\right] = \left[ \begin{array}{ccc} 11 & 8 & 20 \\ 8 & 18 & 19 \\ 20 & 19 & 38 \end{array}\right]$$

$$\left[ \begin{array}{ccc} 26 & 11 & 22 \\ 11 & 6 & 14 \\ 22 & 14 & 35 \end{array}\right] \ne \left[ \begin{array}{ccc} 11 & 8 & 20 \\ 8 & 18 & 19 \\ 20 & 19 & 38 \end{array}\right], therefore ~A^TA \ne AA^T$$

#### (2) For a special type of square matrix A, we get $A^TA = AA^T$. Under what conditions could this be true? (Hint: The Identity matrix I is an example of such matrix).

When a matrix can be inverted, it holds true. For example:
```{r}
A <- matrix(c(1, 2, 2, 4), nrow = 2)
identical(A %*% t(A), t(A) %*% A)
```

# Problem Set 2

Matrix factorization is a very important problem. There are supercomputers built just to do matrix factorization. Every second you are on an airplane, matrices are being factorized. Radars that track flights use a technique called Kalman filtering. At the heart of Kalman Filtering is a Matrix Factorization operation. Kalman Filters are solving linear systems of equations when they track your flight using radars. Write an R function to factorize a square matrix A into LU or LDU, whichever you prefer.

```{r}
A <- matrix(rexp(25), ncol = 5)

LU.decomp <- function(A){
  # The creation of upper matrix U starts with the original matrix A
  U = A
  n = nrow(U)
  L = diag(1, ncol(A), nrow(A)) 
  # https://stackoverflow.com/questions/7102117/how-to-create-a-diagonal-matrix-in-r
  
  # In order to loop through two rows at a time, the first loop must complete at n-1
  # https://stackoverflow.com/questions/27802246/how-to-loop-through-a-matrix-rows-from-in-and-columns
  for (i in 1:(n - 1)){
    
    for (j in (i + 1):n){
      
      if (U[i, i] != 0){
        
        L[j, i] <- U[j, i] / U[i, i]
        
        U[j, ] <- U[j, ] - L[j, i] * U[i, ]
        
      }
    }
  }
  print("Lower Matrix L")
  print(L) 
  print("Upper Matrix U")
  print(U)
  print("L * U")
  print(L%*%U)
}

```

Finally, let's print the original matrix followed by the function's output of the Lower, Upper, and L*U
```{r}
A

LU.decomp(A)

```
The output confirms A=LU
